# ACR 2017 abstract

Build tables for Atul's 2017 ACR abstract.
Collects code chunks from `summarizePrevalence.Rmd` and `summarizeIncidence.Rmd`.

* Title
  * **Do TNF Inhibitors Reduce the Incidence of Cardiac, Pulmonary and Neurologic Comorbidities in Ankylosing Spondylitis? An Analysis of Three Large US Claims Databases.**
* Authors
  * Atul Deodhar, Kevin Winthrop, Benjamin Chan, Sarah Siegel, Jeffery Stark, Robert Suruki, Rhonda Bohn, Huifeng Yun, Lang Chen, Jeffery Curtis


## Prevalence

```{r}
df <-
  "../data/processed/queryPrevalentComorbidities.csv" %>% 
  read.csv(file = ., na.string = c("NA", "")) %>% 
  rename(disease = Disease)
foo <- function(db, exp) {
    col <- which(names(df) %in% c("database", "outcomeCategory", "disease", "prevPct"))
    df %>% 
      filter(timeWindow == "Prior to index") %>% 
      filter(database == db) %>% 
      filter(exposure == exp) %>% 
      select(col)
}
df1a <- foo("MPCD", "NSAID or no exposure")
df1b <- foo("MPCD", "DMARD")
df1c <- foo("MPCD", "TNF")
df2a <- foo("Marketscan", "NSAID or no exposure")
df2b <- foo("Marketscan", "DMARD")
df2c <- foo("Marketscan", "TNF")
df3a <- foo("Medicare", "NSAID or no exposure")
df3b <- foo("Medicare", "DMARD")
df3c <- foo("Medicare", "TNF")
foo <- function (a, b, c) {
    by <- c("database", "outcomeCategory", "disease")
    merge(a, 
          merge(b, 
                c, 
                by = by, all = TRUE, suffixes = c("_DMARD", "_TNF")), 
          by = by, all = TRUE) %>% 
      rename(prevPct_NSAID = prevPct) %>% 
      select(-c(database))
}
prev <- 
  merge(foo(df1a, df1b, df1c), 
        merge(foo(df2a, df2b, df2c),
              foo(df3a, df3b, df3c),
              by = c("outcomeCategory", "disease"),
              all = TRUE,
              suffixes = c("_Marketscan", "_Medicare")),
        by = c("outcomeCategory", "disease"),
        all = TRUE) %>% 
  rename(prevPct_NSAID_MPCD = prevPct_NSAID,
         prevPct_DMARD_MPCD = prevPct_DMARD,
         prevPct_TNF_MPCD = prevPct_TNF) %>%
  select(c(outcomeCategory, disease,
           prevPct_TNF_MPCD, prevPct_DMARD_MPCD, prevPct_NSAID_MPCD,
           prevPct_TNF_Marketscan, prevPct_DMARD_Marketscan, prevPct_NSAID_Marketscan,
           prevPct_TNF_Medicare, prevPct_DMARD_Medicare, prevPct_NSAID_Medicare)) %>% 
  rename("MPCD NSAID or no exposure" = prevPct_NSAID_MPCD,
         "MPCD DMARD" = prevPct_DMARD_MPCD,
         "MPCD TNF" = prevPct_TNF_MPCD,
         "Marketscan NSAID or no exposure" = prevPct_NSAID_Marketscan,
         "Marketscan DMARD" = prevPct_DMARD_Marketscan,
         "Marketscan TNF" = prevPct_TNF_Marketscan,
         "Medicare NSAID or no exposure" = prevPct_NSAID_Medicare,
         "Medicare DMARD" = prevPct_DMARD_Medicare,
         "Medicare TNF" = prevPct_TNF_Medicare)
prev[is.na(prev)] <- 0
prev %>% kable(digits = 1)
```


## Incidence

```{r}
df <-
  "../data/processed/queryIncidenceOutcomes.csv" %>% 
  read.csv(file = ., na.string = c("NA", "")) %>% 
  rename(disease = Disease)
foo <- function (db, exp) {
  require(magrittr)
  require(dplyr)
  compare <-
    bind_rows(compareIncidenceRates(db, exp, "Cardiac disease", "Aortic Insufficiency/Aortic Regurgitation"),
              compareIncidenceRates(db, exp, "Cardiac disease", "Conduction Block"),
              compareIncidenceRates(db, exp, "Cardiac disease", "Myocardial infarction"),
              compareIncidenceRates(db, exp, "Lung disease", "Restrictive lung disease"),
              compareIncidenceRates(db, exp, "Neurological Disease", "Spinal Cord compression"),
              compareIncidenceRates(db, exp, "PsO/PsA", "Psoriasis"),
              compareIncidenceRates(db, exp, "Inflammatory bowel disease", "Crohn.s Disease"),
              compareIncidenceRates(db, exp, "Inflammatory bowel disease", "Ulcerative Colitis"),
              compareIncidenceRates(db, exp, "Uveitis", "Uveitis")) %>% 
    select(c(outcomeCategory, disease, rate1, rate2, pValue))
  names(compare) <- sub("rate1", sprintf("%s %s", db, exp[1]), names(compare))
  names(compare) <- sub("rate2", sprintf("%s %s", db, exp[2]), names(compare))
  names(compare) <- sub("pValue", sprintf("%s p-value", db), names(compare))
  compare
}
bar <- function () {
  merge(foo("MPCD", exp), 
        merge(foo("Marketscan", exp), 
              foo("Medicare", exp), 
              by = c("outcomeCategory", "disease")),
        by = c("outcomeCategory", "disease"))
}
exp <- c("TNF", "NSAID or no exposure")
inc <- bar()
inc[is.na(inc)] <- 0
inc %>% kable(digits = c(rep(0, 2), rep(c(1, 1, 3), 3)))
exp <- c("TNF", "DMARD")
inc <- bar()
inc[is.na(inc)] <- 0
inc %>% kable(digits = c(rep(0, 2), rep(c(1, 1, 3), 3)))
```
