# ACR 2017 abstract

Build tables for Atul's 2017 ACR abstract.
Collects code chunks from `summarizePrevalence.Rmd` and `summarizeIncidence.Rmd`.

* Title
  * **Do TNF Inhibitors Reduce the Incidence of Cardiac, Pulmonary and Neurologic Comorbidities in Ankylosing Spondylitis? An Analysis of Three Large US Claims Databases.**
* Authors
  * Atul Deodhar, Kevin Winthrop, Benjamin Chan, Sarah Siegel, Jeffery Stark, Robert Suruki, Rhonda Bohn, Huifeng Yun, Lang Chen, Jeffery Curtis


## Prevalence

```{r}
df <-
  "../data/processed/queryPrevalentComorbidities.csv" %>% 
  read.csv(file = ., na.string = c("NA", "")) %>% 
  rename(disease = Disease)
foo <- function(db, exp) {
    col <- which(names(df) %in% c("database", "outcomeCategory", "timeWindow", "disease", "prevPct"))
    df %>% 
      filter(timeWindow == "12 months") %>% 
      mutate(timeWindow = "12-month (6-month baseline to 6-month follow-up)") %>% 
      filter(database == db) %>% 
      filter(exposure == exp) %>% 
      select(col)
}
df1a <- foo("MPCD", "NSAID or no exposure")
df1b <- foo("MPCD", "DMARD")
df1c <- foo("MPCD", "TNF")
df2a <- foo("Marketscan", "NSAID or no exposure")
df2b <- foo("Marketscan", "DMARD")
df2c <- foo("Marketscan", "TNF")
df3a <- foo("Medicare", "NSAID or no exposure")
df3b <- foo("Medicare", "DMARD")
df3c <- foo("Medicare", "TNF")
by <- c("database", "outcomeCategory", "disease", "timeWindow")
foo <- function (a, b, c) {
    merge(a, 
          merge(b, 
                c, 
                by = by, all = TRUE, suffixes = c("_DMARD", "_TNF")), 
          by = by, all = TRUE) %>% 
      rename(prevPct_NSAID = prevPct) %>% 
      select(-c(database))
}
prev <- 
  merge(foo(df1a, df1b, df1c), 
        merge(foo(df2a, df2b, df2c),
              foo(df3a, df3b, df3c),
              by = by[2:length(by)],
              all = TRUE,
              suffixes = c("_Marketscan", "_Medicare")),
        by = by[2:length(by)],
        all = TRUE) %>% 
  rename(prevPct_NSAID_MPCD = prevPct_NSAID,
         prevPct_DMARD_MPCD = prevPct_DMARD,
         prevPct_TNF_MPCD = prevPct_TNF) %>%
  select(c(outcomeCategory, disease, timeWindow,
           prevPct_TNF_MPCD, prevPct_DMARD_MPCD, prevPct_NSAID_MPCD,
           prevPct_TNF_Marketscan, prevPct_DMARD_Marketscan, prevPct_NSAID_Marketscan,
           prevPct_TNF_Medicare, prevPct_DMARD_Medicare, prevPct_NSAID_Medicare)) %>% 
  rename("MPCD NSAID or no exposure" = prevPct_NSAID_MPCD,
         "MPCD DMARD" = prevPct_DMARD_MPCD,
         "MPCD TNF" = prevPct_TNF_MPCD,
         "Marketscan NSAID or no exposure" = prevPct_NSAID_Marketscan,
         "Marketscan DMARD" = prevPct_DMARD_Marketscan,
         "Marketscan TNF" = prevPct_TNF_Marketscan,
         "Medicare NSAID or no exposure" = prevPct_NSAID_Medicare,
         "Medicare DMARD" = prevPct_DMARD_Medicare,
         "Medicare TNF" = prevPct_TNF_Medicare)
prev[is.na(prev)] <- 0
prev %>% kable(digits = 1)
```


## Incidence

```{r}
df <-
  "../data/processed/queryIncidenceOutcomes.csv" %>% 
  read.csv(file = ., na.string = c("NA", "")) %>% 
  rename(disease = Disease)
foo <- function (db, exp) {
  require(magrittr)
  require(dplyr)
  compare <-
    bind_rows(compareIncidenceRates(db, exp, "Cancer", "Hematologic Cancer"),
              compareIncidenceRates(db, exp, "Cancer", "Non Melanoma Skin Cancer"),
              compareIncidenceRates(db, exp, "Cancer", "Solid Cancer"),
              compareIncidenceRates(db, exp, "Cardiac disease", "Aortic Insufficiency/Aortic Regurgitation"),
              compareIncidenceRates(db, exp, "Cardiac disease", "Conduction Block"),
              compareIncidenceRates(db, exp, "Cardiac disease", "Myocardial infarction"),
              compareIncidenceRates(db, exp, "Infection", "Hospitalized infection"),
              compareIncidenceRates(db, exp, "Infection", "Opportunistic infection"),
              compareIncidenceRates(db, exp, "Inflammatory bowel disease", "Crohn.s Disease"),
              compareIncidenceRates(db, exp, "Inflammatory bowel disease", "Ulcerative Colitis"),
              compareIncidenceRates(db, exp, "Kidney disease", "Amyloidosis"),
              compareIncidenceRates(db, exp, "Kidney disease", "IgA nephropathy"),
              compareIncidenceRates(db, exp, "Kidney disease", "Nephrotic syndrome"),
              compareIncidenceRates(db, exp, "Lung disease", "Apical Pulmonary fibrosis"),
              compareIncidenceRates(db, exp, "Lung disease", "Interstitial lung disease"),
              compareIncidenceRates(db, exp, "Lung disease", "Restrictive lung disease"),
              compareIncidenceRates(db, exp, "Neurological Disease", "Cauda Equina syndrome"),
              compareIncidenceRates(db, exp, "Neurological Disease", "Spinal Cord compression"),
              compareIncidenceRates(db, exp, "PsO/PsA", "Psoriasis"),
              compareIncidenceRates(db, exp, "PsO/PsA", "Psoriatic arthritis"),
              compareIncidenceRates(db, exp, "Uveitis", "Uveitis")) %>% 
    select(c(outcomeCategory, disease, rate1, rate2, pValue)) %>%
    mutate(pValue = case_when(.$pValue > 0.05 ~ "NS",
                              .$pValue < 0.001 ~ "<0.001",
                              TRUE ~ sprintf("%.03f", .$pValue)))
  names(compare) <- sub("rate1", sprintf("%s %s", db, exp[1]), names(compare))
  names(compare) <- sub("rate2", sprintf("%s %s", db, exp[2]), names(compare))
  names(compare) <- sub("pValue", sprintf("%s p-value", db), names(compare))
  compare
}
bar <- function () {
  merge(foo("MPCD", exp), 
        merge(foo("Marketscan", exp), 
              foo("Medicare", exp), 
              by = c("outcomeCategory", "disease")),
        by = c("outcomeCategory", "disease"))
}
exp <- c("TNF", "NSAID or no exposure")
inc <- bar()
inc[is.na(inc)] <- 0
inc %>% kable(digits = c(rep(0, 2), rep(c(1, 1, 3), 3)))
exp <- c("TNF", "DMARD")
inc <- bar()
inc[is.na(inc)] <- 0
inc %>% kable(digits = c(rep(0, 2), rep(c(1, 1, 3), 3)))
```
