# Plot prevalence

```
From: Curtis, Jeffrey R [mailto:jrcurtis@uabmc.edu] 
Sent: Thursday, May 11, 2017 10:59 AM
Subject: Table 1 Distribution of Characteristics of AS cohort by data source 1 year baseline

Here is table shell for table 1 for AS cohort. All covariates are measured in
baseline, although I think that we should have additional rows added for all
13 outcomes of interest, using all available leftward data (not just
baseline). So for example, someone who had history of uveitis, or cancer,
would appear as rows in this table.

This would be the same format for Aim II that provides the corresponding
information with each column representing the exposure episodes.
```

Read prevalence data.
See `queryPrevalentComorbidities.sas`.

```{r}
df <-
  "../data/processed/queryPrevalentComorbidities.csv" %>% 
  read.csv(file = ., na.string = c("NA", ""))
```

Plot using `plotPrev()`.

* MPCD [PNG](../figures/queryPrevalentComorbiditiesMPCD.png), [SVG](../figures/queryPrevalentComorbiditiesMPCD.svg)
* Marketscan [PNG](../figures/queryPrevalentComorbiditiesMarketscan.png), [SVG](../figures/queryPrevalentComorbiditiesMarketscan.svg)
* Medicare [PNG](../figures/queryPrevalentComorbiditiesMedicare.png), [SVG](../figures/queryPrevalentComorbiditiesMedicare.svg)

```{r}
w <- 6
h <- 33
"../figures/queryPrevalentComorbiditiesMPCD.png" %>% 
  ggsave(., plotPrev("MPCD"), width = w, height = h, units = "in", dpi = 300)
"../figures/queryPrevalentComorbiditiesMPCD.svg" %>% 
  ggsave(., plotPrev("MPCD"), width = w, height = h, units = "in", dpi = 300)
"../figures/queryPrevalentComorbiditiesMarketscan.png" %>% 
  ggsave(., plotPrev("Marketscan"), width = w, height = h, units = "in", dpi = 300)
"../figures/queryPrevalentComorbiditiesMarketscan.svg" %>% 
  ggsave(., plotPrev("Marketscan"), width = w, height = h, units = "in", dpi = 300)
"../figures/queryPrevalentComorbiditiesMedicare.png" %>% 
  ggsave(., plotPrev("Medicare"), width = w, height = h, units = "in", dpi = 300)
"../figures/queryPrevalentComorbiditiesMedicare.svg" %>% 
  ggsave(., plotPrev("Medicare"), width = w, height = h, units = "in", dpi = 300)
```
